### 2020-06-25 docs/LaTex/Paper.tex
Sorting files and folders

  // prepare upstream data transmission at the next possible time.
  // transmit on port 1 (the first parameter); you can use any value from 1 to 223 (others are reserved).
  // don't request an ack (the last parameter, if not zero, requests an ack from the network).
  // Remember, acks consume a lot of network resources; don't ask for an ack unless you really need it.

  lpp.reset();
  lpp.addAnalogInput(1, potVal);

  LMIC_setTxData2(1, lpp.getBuffer(), lpp.getSize(), 0);
  Serial.println(F("Packet queued"));
\end{lstlisting}

So, as can be seen, in order to prepare the payload firstly the analog pin is stored in \cmd{potVal} variable, after this the function \cmd{lpp.reset()} is ued to reset the CayenneLPP buffer, then the measure \cmd{potVal} is added to the CayenneLPP buffer in the first channel using the function \cmd{lpp.addAnalogInput()}, finally the  \doubt{REDO}
%So, as can be seen, in order to prepare the payload, the first is to read the analog pin and store the read value in \cmd{potVal} variable ---which is a \cmd{double} type and this makes no difference with \cmd{float} type in \enquote{On the Uno and other ATMEGA based boards} but it makes \enquote{On the Arduino Due} \cite{Ard_double_type}--- after this, the \cmd{potVal} variable is scaled to a $[0,1.0)$ range, this is due the function \cmd{LMIC\_f2sflt16()} (line 195), which is essentially a kind of encoder to encode floats to 16-bit fields. The working of this function is explained in \cite{MCCI_lmic_16bitencoder}.\footnote{A javascript decoder is also provided by the \href{https://github.com/mcci-catena/arduino-lmic\#uflt16-javascript-decoder}{\cmd{README.md}} but \doubt{it will be described in next sections.}}

@@

\begin{lstlisting}[%
  % float=ht,
  language=cpp,
  firstnumber=248,
  caption={Channels setup.},
  label=ej:chan_setup
  ]
  LMIC_setupChannel(0, 868100000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(1, 868300000, DR_RANGE_MAP(DR_SF12, DR_SF7B), BAND_CENTI);  // g-band
  LMIC_setupChannel(2, 868500000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(3, 867100000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(4, 867300000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(5, 867500000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(6, 867700000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(7, 867900000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(8, 868800000, DR_RANGE_MAP(DR_FSK,  DR_FSK),  BAND_MILLI);  // g2-band
\end{lstlisting}

>>>>

  // Reset CayenneLPP buffer
  lpp.reset();

  // Add the measured value to CayenneLPP buffer
  lpp.addAnalogInput(1, potVal);

  // prepare upstream data transmission at the next possible time.
  // transmit on port 1 (the first parameter); you can use any value from 1 to 223 (others are reserved).
  // don't request an ack (the last parameter, if not zero, requests an ack from the network).
  // Remember, acks consume a lot of network resources; don't ask for an ack unless you really need it.
  LMIC_setTxData2(1, lpp.getBuffer(), lpp.getSize(), 0);
  Serial.println(F("Packet queued"));
\end{lstlisting}

So, as can be seen, in order to prepare the payload firstly the analog pin is stored in \cmd{potVal} variable, after this the function \cmd{lpp.reset()} is ued to reset the CayenneLPP buffer, then the measure \cmd{potVal} is added to the CayenneLPP buffer in the first channel using the function \cmd{lpp.addAnalogInput()}, finally the buffer content is prepared to be transmitted at the next possible time.
%So, as can be seen, in order to prepare the payload, the first is to read the analog pin and store the read value in \cmd{potVal} variable ---which is a \cmd{double} type and this makes no difference with \cmd{float} type in \enquote{On the Uno and other ATMEGA based boards} but it makes \enquote{On the Arduino Due} \cite{Ard_double_type}--- after this, the \cmd{potVal} variable is scaled to a $[0,1.0)$ range, this is due the function \cmd{LMIC\_f2sflt16()} (line 195), which is essentially a kind of encoder to encode floats to 16-bit fields. The working of this function is explained in \cite{MCCI_lmic_16bitencoder}.\footnote{A javascript decoder is also provided by the \href{https://github.com/mcci-catena/arduino-lmic\#uflt16-javascript-decoder}{\cmd{README.md}} but \doubt{it will be described in next sections.}}

@@

\begin{lstlisting}[%
  % float=ht,
  language=cpp,
  firstnumber=250,
  caption={Channels setup.},
  label=ej:chan_setup
  ]
  LMIC_setupChannel(0, 868100000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(1, 868300000, DR_RANGE_MAP(DR_SF12, DR_SF7B), BAND_CENTI);  // g-band
  LMIC_setupChannel(2, 868500000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(3, 867100000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(4, 867300000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(5, 867500000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(6, 867700000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(7, 867900000, DR_RANGE_MAP(DR_SF12, DR_SF7),  BAND_CENTI);  // g-band
  LMIC_setupChannel(8, 868800000, DR_RANGE_MAP(DR_FSK,  DR_FSK),  BAND_MILLI);  // g2-band
\end{lstlisting}
